\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-24 document/XSGRB_sample.tex
GRB100205A, GRB100219A and GRB100316B

\newcommand{\griz}{$g' r' i' z'$}
\newcommand{\JHK}{$JHK_{\rm{s}}$}
\newcommand{\gK}{$g' r' i' z' JHK_{\rm{s}}$}
\newcommand{\Msun}{$M_\odot$}
\newcommand{\lya}{Ly$\alpha$} 
\newcommand{\lyb}{Ly$\beta$} 
\newcommand{\hb}{H$\beta$} 
\newcommand{\ha}{H$\alpha$} 
\newcommand{\oi}{[\ion{O}{1}]} 
\newcommand{\sii}{[\ion{S}{2}]} 
\newcommand{\oii}{[\ion{O}{2}]$\lambda$3727} 
\newcommand{\oiii}{[\ion{O}{3}]$\lambda$5007}
\newcommand{\nii}{[\ion{N}{2}]} 
\newcommand{\feii}{\ion{Fe}{2}} 
\newcommand{\civ}{\ion{C}{4}} 
\newcommand{\cii}{\ion{C}{2}}
\newcommand{\mgii}{\ion{Mg}{2}} 
\newcommand{\hi}{\ion{H}{1}} 
\newcommand{\ali}{\ion{Al}{1}} 
\newcommand{\SIii}{\ion{Si}{2}} 
\begin{document}

@@

	\subsection{GRB100724A* (z = 1.288)}
	The data presented here also formed the basis of GCN \#
	10971\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10971.gcn3}}. 
	The spectrum has not otherwise been published previously. The observations were
	carried out in RRM starting 11 min after the GRB trigger. 
	See section \ref{RRM}, for a description of the RRM scheme.
	Absorption lines from several ionic species are detected in the afterglow continuum at a common redshift
	of $z = 1.288$. This burst is not a part of the statistical sample.

@@

	\subsection{GRB130606A (z = 5.913)}
	The data presented here also formed the basis of GCN \#
	14816\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14816.gcn3}} and is published
	in \citet{Hartoog2015}.
	The observations consists of three 2x600sec visits starting 7.1 hr after the burst at fairly
	high airmass.
	We detect absorption features from a wide range of ions at z=5.913 
	as well as intervening absorption at $z=2.313, 2.521, 3.415, 4.6448, 4.6468, 4 and 4.6495$.

	\subsection{GRB151021A (z = 2.330)}
	The data presented here also formed the basis of GCN \#
	18426\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/18982.gcn3}} and is not published
	elsewhere.
	The observation was carried out in RRM starting 44 min af the GRB trigger.
	We detect absorption features from a wide range of ions at z=2.330 
	as well as intervening absorption at $z=1.49$.

	\subsection{GRB160203A (z = 3.517)}
	The data presented here also formed the basis of GCN \#
	18982\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/18982.gcn3}} and is not published
	elsewhere.
	The observation was carried out in RRM starting 18 min after the GRB trigger.
	We detect absorption features from a wide range of ions at z=3.517 
	as well as intervening absorption at $z=2.203$.

>>>>

\newcommand{\griz}{$g' r' i' z'$}
\newcommand{\JHK}{$JHK_{\rm{s}}$}
\newcommand{\gK}{$g' r' i' z' JHK_{\rm{s}}$}
\newcommand{\Msun}{$M_\odot$}
\newcommand{\lya}{Ly$\alpha$} 
\newcommand{\lyb}{Ly$\beta$} 
\newcommand{\hb}{H$\beta$} 
\newcommand{\ha}{H$\alpha$} 
\newcommand{\oi}{[\ion{O}{1}]} 
\newcommand{\sii}{[\ion{S}{2}]} 
\newcommand{\oii}{[\ion{O}{2}]$\lambda$3727} 
\newcommand{\oiii}{[\ion{O}{3}]$\lambda$5007}
\newcommand{\nii}{[\ion{N}{2}]} 
\newcommand{\feii}{\ion{Fe}{2}} 
\newcommand{\civ}{\ion{C}{4}} 
\newcommand{\cii}{\ion{C}{2}}
\newcommand{\mgi}{\ion{Mg}{1}} 
\newcommand{\mgii}{\ion{Mg}{2}} 
\newcommand{\hi}{\ion{H}{1}} 
\newcommand{\ali}{\ion{Al}{1}} 
\newcommand{\alii}{\ion{Al}{2}} 
\newcommand{\aliii}{\ion{Al}{3}} 
\newcommand{\SIii}{\ion{Si}{2}} 
\begin{document}

@@

	\subsection{GRB100205A}
	Observed 3 days after the \textit{Swift} trigger. No afterglow or host detected in 10.8 ks. GRB likely located at high redshift\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10399.gcn3}}.

	\subsection{GRB100219A (z = 4.667)}
	The data presented here also formed the basis of GCN \#
	10441\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10441.gcn3}} and is published
	in \citet{Thone2013}.
	Observations started 12.5 hours after the \textit{Swift} trigger and has a
	total exposure time of 4.8 ks.
	Absorption features, including those of \lya, from a multitude of ions are
	detected against the afterglow continuum at $z = 4.667$. Additionally,
	absorption from an intervening system is found at $z = 2.181$.

	\subsection{GRB100316B (z = 1.180)}
	The data presented here also formed the basis of GCN \#
	10495\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10495.gcn3}}.
	Observations started 44 minutes after the \textit{Swift} trigger and has a
	total exposure time of 2.4 ks.
	Absorption features from \feii, \alii, \aliii,	\mgii~and \mgi~are well detected against the afterglow continuum at $z = 1.180$. Additionally, strong absorption lines from \feii~and \mgii~from an intervening system are found at $z = 1.063$.

	\subsection{GRB100724A* (z = 1.288)}
	The data presented here also formed the basis of GCN \#
	10971\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10971.gcn3}}. 
	The spectrum has not otherwise been published previously. The observations were
	carried out in RRM starting 11 min after the GRB trigger. 
	See section \ref{RRM}, for a description of the RRM scheme.
	Absorption lines from several ionic species are detected in the afterglow
	continuum at a common redshift of $z = 1.288$.
	This burst has been flux calibrated using the master response function and is
	not a part of the statistical sample.

@@

	\subsection{GRB130606A (z = 5.913)}
	The data presented here also formed the basis of GCN \#
	14816\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14816.gcn3}} and is published
	in \citet{Hartoog2015}.
	The observations consists of three 2x600sec visits starting 7.1 hr after the burst at fairly
	high airmass.
	We detect absorption features from a wide range of ions at $z=5.913$
	as well as intervening absorption at $z=2.313, 2.521, 3.415, 4.6448, 4.6468, 4 and 4.6495$.

	\subsection{GRB151021A (z = 2.330)}
	The data presented here also formed the basis of GCN \#
	18426\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/18982.gcn3}} and is not published
	elsewhere.
	The observation was carried out in RRM starting 44 min af the GRB trigger.
	We detect absorption features from a wide range of ions at $z=2.330$ 
	as well as intervening absorption at $z=1.49$.

	\subsection{GRB160203A (z = 3.517)}
	The data presented here also formed the basis of GCN \#
	18982\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/18982.gcn3}} and is not published
	elsewhere.
	The observation was carried out in RRM starting 18 min after the GRB trigger.
	We detect absorption features from a wide range of ions at $z=3.517$ 
	as well as intervening absorption at $z=2.203$.
